---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# FishApp

<!-- badges: start -->
[![Lifecycle: experimental](https://img.shields.io/badge/lifecycle-experimental-orange.svg)](https://lifecycle.r-lib.org/articles/stages.html#experimental)
<!-- badges: end -->

An improved description is under development...

## Installation

For now, install and test FishApp by cloning this repository, creating an R project inside it, and calling the following functions:
```{r}
devtools::load_all()
run_app()
```

Once the repository is set up, you can gather and view new changes to the app by calling `git pull` from the terminal (or from inside Rstudio), and then calling the same two functions as above.

<!-- You can install the development version of FishApp like so: -->

<!-- ``` r -->

<!-- ``` -->

<!-- ## Example -->

<!-- This is a basic example which shows you how to solve a common problem: -->

<!-- ```{r example} -->
<!-- library(FishApp) -->
<!-- ## basic example code -->
<!-- ``` -->
